% !TEX encoding = UTF-8 Unicode
\documentclass{friggeri-cv}

\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[english]{babel}
\usepackage{fontawesome}


\begin{document}

  \header{Dixing}{Xu}{research \{ engineer, assistant \}}

  \section{social}

    \begin{center}
        \renewcommand{\arraystretch}{1.5}
        \begin{tabular}{ p{16em} p{16em} p{16em} }
          \href{https://dex.moe}{\faHome\quad Website: dex.moe}
          &
          \href{tel:+86 18013518265}{\faPhone\quad Phone: +86 18013518265}
          &
          \href{mailto:dixingxu@gmail.com}{\faEnvelope\quad Email: dixingxu@gmail.com}
          \\
          \href{https://github.com/dexhunter}{\faGithub\quad GitHub: @dexhunter}
          &
          \href{https://linkedin.com/in/dex-xu}{\faLinkedin\quad LinkedIn: Dixing Xu}
          &
          \href{https://scholar.google.co.jp/citations?user=8Ez_u30AAAAJ&hl=en}{\faGraduationCap\quad Scholar: Dixing (Dex) Xu}
          \\ \\
        \end{tabular}
      \end{center}

  \section{cover letter}

  \vspace{5mm}

  \noindent To whom it may concern,


  \paragraph{}
  I am writing to express my interest in the research engineer position in the Department of Information Systems, Singapore Management University.

  \paragraph{}
  As you can see on my \href{resume.dex.moe}{\textbf{Curriculum Vitae}}, I am in my final year at Xi'an Jiaotong-Liverpool University in Suzhou, China. I am going to obtain my Bachelor of Science in Information and Computing Sciences in July, 2020. Previously, I have worked as a research assistant at Nanyang Technological University, Singapore under supervision of Prof. Rui Tan and I am currently a visiting student researcher at Zhejiang University, Hangzhou, China. My research mostly focuses on deep learning and its applications. I have worked with team transferring the technology to different fields including quantitative finance/algorithmic trading, anime/arts, privacy, electrical systems and so on. My current research is going around the field of security on various systems such as blockchain \& smart contracts, industrial control systems and many more. I have also contributed to multiple open-source projects which can be seen from my \href{github.com/dexhunter}{\textbf{Github profile}}.

  \paragraph{}
  Thank you for considering my application.

  \vspace{10mm}

  \noindent Sincerely,
  \newline Dixing (Dex) Xu.

\end{document}
